\addchap*{Acknowledgments}

My thesis ended up taking much longer than planned for a variety of reasons, some of which legitimate, others my excuses for procrastination. In any case, that has only made me more grateful to the people without whose support it would not have been possible, namely my advisors, friends and family.

First and foremost, my advisors. To Michael, thank you for taking over the advising duties at moment's notice and for being so generous with your time even when with an inconvenient 6-hour time difference. Thank you for helping me find clarity in this chaotic, certainly high-entropy topic, without your expertise and insight this thesis would look a lot different. To Lucia, thank you for staying on as my advisor despite the many changes in topic, direction and methodology, for being always engaging in meetings, providing valuable and, if needed, candid feedback that keeps my runaway theoretical nihilism in check. To Annemarie, thank you for working with me from the scratch and helping me develop a vague idea, step by step, into a manageable thesis project. I may never have found myself working on this fascinating topic of valency without you.

Another round of thanks goes to my friends at the LST department in Saarbrücken. To Alina, Leonie and Rricha, thank you for the camaraderie of going through the thesis writing process together. To Ben, thank you for being a good friend for what feels like a lot longer than 2 years, and for putting me up last minute during my quick trip back to finish the thesis. To Katharina, Li Meng, Sharmilla, Niyati and all my other friends, thank you for your support and friendship that made my almost three-year sojourn in Saarbrücken a lot more enjoyable.

Finally, I would like to thank my parents for their unconditional support and love. You are always there for me when I need it, and you cheer me on for my thesis even if you still have no idea what verbal valency or information theory is :-)

Thank you all from the bottom of my heart.

